Notes on the Godunov Step in {\tt MAESTRO} and {\tt VARDEN}

### 2008-04-17 docs/Godunov_notes/paper.tex
more work on varden umac section

\section{Computing $\Ub^{\edge}$ and $s^{\edge}$ in {\tt VARDEN}}
\section{Notes on {\tt enthalpy\_pred\_type} in {\tt MAESTRO}}
\begin{table*}
\begin{center}
\caption{Forcing term into make edge scal \newline}
\begin{tabular}{|c|c|c|}
\multicolumn{1}{c}{PRED X}   & \multicolumn{1}{c}{Force} \\
\hline
  &   \\
T $(X)$ & $0$ \\
  &   \\
T $(\rho^\prime)$ & $-\rho^\prime \; \nabla \cdot (\ut+w_0 \eb_r) - \nabla \cdot (\ut \rho_0) $  \\
  &   \\
\hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|c|c|}
\multicolumn{1}{c}{H PRED TYPE}   & \multicolumn{1}{c}{Force} \\
\hline
   & \\
 1 $((\rho h)^\prime)$ &  $(\tilde{w} \frac{\partial p_0}{\partial r}) - (\rho h)^\prime \; \nabla \cdot (\ut+w_0 \eb_r) - \nabla \cdot (\ut (\rho h)_0) $  \\
   & \\
 2 $(h)$ & $\frac{1}{\rho} (\psi + \tilde{w} \frac{\partial p_0}{\partial r})$  \\
   & \\
 3 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
 4 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

We do a 1D Taylor series extrapolation to get both components of velocity at the x-face:
\Ub_{L,\ib-\half\eb_x}^{1D} &=& \Ub_{\ib-\eb_x} + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}\right){\rm max}(0,\Delta_x\Ub_{\ib-\eb_x}), \\
\Ub_{R,\ib-\half\eb_x}^{1D} &=& \Ub_{\ib} + \left(\half - \frac{\dt}{2h}u_{\ib}\right){\rm min}(0,\Delta_x\Ub_{\ib}).
The normal velocity Riemann problem is:
0, & (u_{L,\ib-\half\eb_x}^{1D} \le 0 ~ {\rm AND} ~ u_{R,\ib-\half\eb_x}^{1D} \ge 0 ~ {\rm OR} ~ |u_{L,\ib-\half\eb_x}^{1D} + u_{R,\ib-\half\eb_x}^{1D}| < \epsilon, \\
u_{L,\ib-\half\eb_x}^{1D}, & u_{L,\ib-\half\eb_x}^{1D} + u_{R,\ib-\half\eb_x}^{1D} > 0, \\
u_{R,\ib-\half\eb_x}^{1D}, & u_{L,\ib-\half\eb_x}^{1D} + u_{R,\ib-\half\eb_x}^{1D} < 0.
We obtain the transverse velocity by upwinding based on $u_{\ib-\half\eb_x}^{1D}$:
v_{\ib-\half\eb_x}^{1D} =
\half(v_{L,\ib-\half\eb_x}^{1D} + v_{R,\ib-\half\eb_x}^{1D}), & \left|u_{\ib-\half\eb_x}^{1D}\right| < \epsilon \\
v_{L,\ib-\half\eb_x}^{1D}, & u_{\ib-\half\eb_x}^{1D} > 0, \\
v_{R,\ib-\half\eb_x}^{1D}, & u_{\ib-\half\eb_x}^{1D} < 0.
Do the exact analogous thing to get both components of velocity at the y-face, $\Ub_{\ib-\half\eb_y}^{1D}$. \\

Now we do a full-dimensional extrapolation to get only the normal velocity at each face:

\subsection{3D Cartesian Case}
\cleardoublepage
\section{Computing $\Ub^{\edge}$ and $s^{\edge}$ in {\tt VARDEN}}
\subsection{2D Cartesian Case}
\subsection{3D Cartesian Case}
\cleardoublepage
\section{Notes on {\tt enthalpy\_pred\_type} in {\tt MAESTRO}}
\begin{table*}
\begin{center}
\caption{Forcing term into make edge scal \newline}
\begin{tabular}{|c|c|c|}
\multicolumn{1}{c}{PRED X}   & \multicolumn{1}{c}{Force} \\
\hline
  &   \\
T $(X)$ & $0$ \\
  &   \\
T $(\rho^\prime)$ & $-\rho^\prime \; \nabla \cdot (\ut+w_0 \eb_r) - \nabla \cdot (\ut \rho_0) $  \\
  &   \\
\hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|c|c|}
\multicolumn{1}{c}{H PRED TYPE}   & \multicolumn{1}{c}{Force} \\
\hline
   & \\
 1 $((\rho h)^\prime)$ &  $(\tilde{w} \frac{\partial p_0}{\partial r}) - (\rho h)^\prime \; \nabla \cdot (\ut+w_0 \eb_r) - \nabla \cdot (\ut (\rho h)_0) $  \\
   & \\
 2 $(h)$ & $\frac{1}{\rho} (\psi + \tilde{w} \frac{\partial p_0}{\partial r})$  \\
   & \\
 3 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
 4 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
\hline
\end{tabular}
\end{center}
\end{table*}
